---
title: "Assignment 2"
author: "Insert My Name"
date: "2024-09-25"
output: html_document # you can change to other output format if you want
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Data Wrangling


## 1.1 (Q1)   

<!-- Include your answers for each question under a second level heading eg ## 1.1 (Q1) -->
**** insert your solutions here *****

```{r}
library(tidyverse)
library(Stat2Data)
data("Hawks")
colnames(Hawks)
# Assume the original data frame is called Hawks
# Create the new data frame hSF with the required columns and conditions
hSF <- Hawks %>%
  filter(Species == "RT" & Weight >= 1000) %>%
  select(Wing, Weight, Tail)           # Select the specified columns
hSF
```

## 1.1 (Q2)   
How many variables does the data frame hSF have? What would you say to communicate this information to a Machine Learning practitioner?

The data frame hSF has 3 variables (or features/columns). These variables are:
Wing: The wing measurement of the hawks.
Weight: The weight of the hawks.
Tail: The tail measurement of the hawks.

To a Machine Learning (ML) practitioner, you can say:
The data frame hSF contains 3 features (variables): Wing, Weight, and Tail. These are the input attributes (or dimensions) of each data point that can be used for model training or analysis.

How many examples does the data frame hSF have? How many observations? How 
many cases?

## 1.2 (Q1)

```{r}
# Sort the hSF data frame by increasing wing span (column "Wing")
hSF_sorted <- hSF %>%
  arrange(Wing)

# Print the top five rows of the sorted data frame
head(hSF_sorted, 5)
```
## 1.3 (Q1)
```{R}
# Create the hawkSpeciesNameCodes data frame
hawkSpeciesNameCodes <- data.frame(
  species_code = c("CH", "RT", "SS"),                    # Species codes
  species_name_full = c("Cooper's", "Red-tailed", "Sharp-shinned")  # Full species names
)

# Print the data frame to check
print(hawkSpeciesNameCodes)
```

```{r}
# Perform a left join to combine Hawks with hawkSpeciesNameCodes
hawksFullName <- Hawks %>%
  left_join(hawkSpeciesNameCodes, by = c("Species" = "species_code")) %>%  # Join on the species code
  select(-Species) %>%  # Remove the original Species column
  rename(Species = species_name_full)  # Rename the new column to Species

# Print the resulting data frame to check
print(hawksFullName)

```


## 1.3 (Q3)
```{r}
# Use select() to choose specific columns and head() to print the top seven rows
top_seven_hawks <- hawksFullName %>%
  select(Species, Wing, Weight) %>%  # Select the specified columns
  head(7)                             # Get the top seven rows

# Print the result
print(top_seven_hawks)
```
## 1.4 (Q1)
```{r}
# Calculate Bird-BMI and create the new data frame
hawksWithBMI <- Hawks %>%
  mutate(Bird_BMI = 1000 * Weight / (Wing^2)) %>%  # Calculate Bird-BMI
  select(Species, Bird_BMI) %>%                     # Select only the Species and Bird-BMI columns
  arrange(desc(Bird_BMI))                           # Arrange in descending order of Bird-BMI

# Print the resulting data frame to check
print(hawksWithBMI)

```

## 1.5 (Q1)
```{r}
# Create the summary table by Hawk species
summary_table <- Hawks %>%
  group_by(Species) %>%  # Group by Hawk species
  summarize(
    num_rows = n(),                                  # Count the number of rows
    mn_wing = mean(Wing, na.rm = TRUE), # na.rm = TRUE: 只对存在的有效数据进行操作  # Calculate the average wing span
    nd_wing = median(Wing, na.rm = TRUE),           # Calculate the median wing span
    t_mn_wing = mean(Wing, trim = 0.1, na.rm = TRUE), # Calculate the trimmed mean wing span
    b_wt_ratio = max(Wing / Tail, na.rm = TRUE)     # Calculate the biggest ratio between wing span and tail length
  )

# Print the summary table to check
print(summary_table)
```

```{r}

```
....

# 2. Random experiments, events and sample spaces, and the set theory

....

# 3. Probability theory

## 3 (Q1)

## 3 (Q2)

.....



